---
title: "p8105_hw1_HL3859"
author: "Hanrui Li"
date: "2024-09-18"
output: github_document
---

## Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.

- `species`: 3 species of penguins (`r unique(penguins$species)`)

- `island`: 3 islands on which the penguins were observed (`r unique(penguins$island)`)

- `bill_length_mm`: The length of the penguin's bill in millimeters ranging from `r range(penguins$bill_length_mm, na.rm = TRUE)[1]` to `r range(penguins$bill_length_mm, na.rm = TRUE)[2]`

- `bill_depth_mm`: The depth of the penguin's bill in millimeters ranging from `r range(penguins$bill_depth_mm, na.rm = TRUE)[1]` to `r range(penguins$bill_depth_mm, na.rm = TRUE)[2]`

- `flipper_length_mm`: The length of the penguin’s flipper in millimeters ranging from `r range(penguins$flipper_length_mm, na.rm = TRUE)[1]` to `r range(penguins$flipper_length_mm, na.rm = TRUE)[2]`

- `body_mass_g`: The body mass of the penguin in grams ranging from `r range(penguins$body_mass_g, na.rm = TRUE)[1]` to `r range(penguins$body_mass_g, na.rm = TRUE)[2]`

- `sex`: The penguins' sex (male or female)

- `year`: Year is from `r range(penguins$year, na.rm = TRUE)[1]` to `r range(penguins$year, na.rm = TRUE)[2]`

- The mean flipper length of the penguins is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` millimeters.

```{r message=FALSE, warning=FALSE}
library(ggplot2)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, colour = species)) + geom_point()
ggsave("scatterplot_hw1.pdf")
```

## Problem 2

```{r}
library(tidyverse)

df = tibble(
  norm_samp = rnorm(10),
  samp_g1 = norm_samp > 0,
  char = sample(letters, 10),
  factor = factor(sample(c("Level1", "Level2", "Level3"), 10, replace = TRUE))
)
df
```

```{r}
library(tidyverse)

df %>% pull(norm_samp) %>% mean()
df %>% pull(samp_g1) %>% mean()
df %>% pull(char) %>% mean()
df %>% pull(factor) %>% mean()
```

Cannot calculate the mean of the character vector and the factor vector because they are not numeric.

```{r}
samp_g1_numeric <- as.numeric(df$samp_g1)

char_numeric <- as.numeric(df$char)

factor_numeric <- as.numeric(df$factor)
```

Logical vectors can be interpreted into numbers 0 and 1, so the mean can be calculated.

Characters cannot be directly interpreted as numbers.

Factor vectors have "level1", "level2", and "level3", which can be interpreted as numbers 1, 2, and 3, so the mean can be calculated.






